The paper on \Large \bf Blockchain Frontrunning

### 2018-09-07 frontrunning/Latex/sections/paper.tex
[frontrunning] drawbacks of commitment schemes + libsubmarine and some other fixes

%______________________________________________________________%
%TODO: Censorship vs frontrunning ! can withholding a transaction be considered as frontrunning? 
%using frontrunning losely, we do not want to defining what exactly front running is, but talking about possibiities of attacks in this nature and also how to prevent these from happening .

@@

\subsubsection{Miners} \labe{minersfrontrunning}
Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this is known as \textbf{transaction reordering} attack.  For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token\ie TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase. So the dishonest miner can step in front of this transaction and place his own buy order ahead. He would simply create his \textit{buy} of 1000 TKN and include it in front of the previous \textit{buy} transaction of 1000 TKN in the block he mines. Doing so, he would receive a better rate than other network users, and afterwards can sell the assets he has bought and gain a price advantage at the expense of others. Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction. In an open source blockchain application, there is no rules on how transactions must be ordered and miners are free to mine transactions in any order they prefer. However, miners can only front-run transactions within the blocks they happen to mine. They could do this also by not broadcasting their own transactions to the network, this makes the miners to be less noticeable to the network when front-running.
Another example here is in the case of decentral exchanges and order cancellation. Every exchange should have the functionality to cancel the orders, especially for a volatile market. In this case, when user decides that her order is not profitable anymore, she would send a cancelation transaction. Here the miner sees the cancelation transaction and puts his own order in front of the cancellation transaction --transaction reordering-- to fill the order, potentially profiting from the order. They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}, see Figure~\ref{MinerFrontrunning}. Front-running can also occur in non-financial smart contracts. As an example, smart contract which adds all the participants to a party invite list, could only be closed by the smart contract owner. In this case when the owner sends the transaction to close the list, a miner can include his own list of participants before the close transaction in the block he mines. This is an issue with the design of the smart contracts and is known as transaction-ordering dependence vulnerability~\cite{luu2016making}.

%TODO: figure for miners reordering attack. it should be just two blocks with transaction inside where the second "modified" one has the orders specifically to profit the miner.

@@

%\subsubsection{Bancor} %TODO: mahsa 
Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk. This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users. Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand. Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.
Recently, researchers have shown that Bancor is vulnerable to front running attacks. Implemented on the Ethereum blockchain, when Bancor transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them. Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for 16s (the average Ethereum blocktime) before being included within a block. This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favourable profits~\cite{BancorIs7:online}. As mentioned in Section~\ref{sec:who can front-run?} and same as every other Ethereum based application, Bancor transactions can be front run by miners and other regular (non-miner) users. There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants \cite{NewTab13:online}.

@@

\noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are are not yet limited to the financial markets. Front-running can occur within other (non-financial) blockchain applications such as naming systems. Blockchain-based domain registrar have been introduced to eliminate the role of central parties \ie domain name system (DNS) which introduce single point of failures in the entire web. One such system is Ghazal, an Ethereum-based naming and PKI system~\cite{moosavighazal}. Ghazal users rely on the Ethereum blockchain to register their \texttt{.ghazal} domain names and bind certificates to those names. In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument. As mentioned before, These transactions will sit in the mempool so that it would be mined by Ethereum miners and included in the block. During this period in which the transaction is not yet confirmed, front-running attack can occur by (i) dishonest miners and/or (ii) regular non-miner user. In the first case, a miner would intercept the \textit{registerdomain} transaction and register that name ahead of the user. A regular non-miner node in the Ethereum network can front-run other user's \textit{registerdomain} at a good profit by paying higher transaction fees. This practice allows the adversarial party  to register an unregistered domain immediately after someone searched for it, and sell the domain name to the users for a higher price. Note that, domain name front-running also occurs in the vanilla system. In this case, front-runners would monitor and identify domain names of interest, and sell it back to the other users with a higher price~\cite{sac022en33:online}.

@@

% PoC of front-running ghazal

@@

%TODO: shayan: connect games to cryptokitties and other collectibles

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.4\linewidth]{figures/cryptokittie842912.png}
\caption{ Cryptokitty Number 842912 \label{fig:cryptokittie}}
\end{figure}

@@

% TODO: also talk about drawbacks, more expensinve, more transactions, UX, forget to reveal.

\subsubsection{Design Decision \#1: Commitment Scheme\newline} %talk about the drawbacks of this scheme: eg: you may forget to reveal. 
Commitment scheme is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}. Commitment scheme is a robust method to prevent information leakage from the sensitive transactions. This could be done by simply broadcasting the hash value of the committed data and later on revealing the values that would be hashed to the committed hash, see Figure~\ref{fig:commitReveal}. 
In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order. Depending on the Dapp design, either the order is collateralized, which means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be considered as a DoS attack. 
Another use of such commitment scheme, is in decentralized naming systems, such as Ghazal or ENS. In this case, a user would send a commit transaction similar to a sealed bid, once the transaction is confirmed and the grace period is over, user would send a reveal transaction revealing the bid and also the details of the requested domain. Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running. Similar approach applies to on-chain voting as well ~\cite{adChainPLCRVoting}, using sealed votes, voters can make sure their votes are hidden until a later date, however their participation and weight of the vote are publicly known. 
Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor. For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, It will be obvious that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme. Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design.

@@

The details of how Submarine commitments work is outside the scope of this paper, however in summary, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address in which no private key exists. By constructing a transaction from that address to the DApp and funding that address we fulfil the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}.

@@

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract. Values V,R and S are set by LocalEtherem to have a valid signature, also the tradeHash uses buyer and seller addresses, mitigating the possibility of front-running by a third party.},label={code:localethereum},float]
    function createEscrow(bytes16 _tradeID, address _seller, address _buyer, uint256 _value, uint16 _fee,
					uint32 _paymentWindowInSeconds, uint32 _expiry, uint8 _v, bytes32 _r, bytes32 _s) 
        payable external {
        bytes32 _tradeHash = keccak256(abi.encodePacked(_tradeID, _seller, _buyer, _value, _fee));
	...
        // A signature (v, r and s) must come from localethereum to open an escrow
        bytes32 _invitationHash = keccak256(abi.encodePacked(
            _tradeHash,
            _paymentWindowInSeconds,
            _expiry
        )); 
\end{lstlisting}

>>>>

@@

\subsubsection{Miners} \label{minersfrontrunning}
Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this is known as \textbf{transaction reordering} attack.  For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token\ie TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase. So the dishonest miner can step in front of this transaction and place his own buy order ahead. He would simply create his \textit{buy} of 1000 TKN and include it in front of the previous \textit{buy} transaction of 1000 TKN in the block he mines. Doing so, he would receive a better rate than other network users, and afterwards can sell the assets he has bought and gain a price advantage at the expense of others. Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction. In an open source blockchain application, there is no rules on how transactions must be ordered and miners are free to mine transactions in any order they prefer. However, miners can only front-run transactions within the blocks they happen to mine. They could do this also by not broadcasting their own transactions to the network, this makes the miners to be less noticeable to the network when front-running.
Another example here is in the case of decentral exchanges and order cancellation. Every exchange should have the functionality to cancel the orders, especially for a volatile market. In this case, when user decides that her order is not profitable anymore, she would send a cancelation transaction. Here the miner sees the cancelation transaction and puts his own order in front of the cancellation transaction --transaction reordering-- to fill the order, potentially profiting from the order. They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}, see Figure~\ref{MinerFrontrunning}. Front-running can also occur in non-financial smart contracts. As an example, smart contract which adds all the participants to a party invite list, could only be closed by the smart contract owner. In this case when the owner sends the transaction to close the list, a miner can include his own list of participants before the close transaction in the block he mines. This is an issue with the design of the smart contracts and is known as transaction-ordering dependence vulnerability~\cite{luu2016making}.

@@

%\subsubsection{Bancor} %TODO: mahsa 
Bancor is an Ethereum-based application that allows users to exchange their tokens without any counter-party risk. This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users. Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand. Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.
Recently, researchers have shown that Bancor is vulnerable to front running attacks. Implemented on the Ethereum blockchain, when Bancor transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them. Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for 16s (the average Ethereum blocktime) before being included within a block. This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favorable profits~\cite{BancorIs7:online}. As mentioned in Section~\ref{sec:who can front-run?} and same as every other Ethereum based application, Bancor transactions can be front run by miners and other regular (non-miner) users. There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants \cite{NewTab13:online}.

@@

\noindent As mentioned in Section~\ref{sec:Front Running on the Blockchains}, although front-running attacks have been more showcased in the context of decentralized exchanges and trading systems, they are not yet limited to the financial markets. Front-running can occur within other (non-financial) blockchain applications such as naming systems. Blockchain-based domain registrar have been introduced to eliminate the role of central parties \ie domain name system (DNS) which introduce single point of failures in the entire web. One such system is Ghazal, an Ethereum-based naming and PKI system~\cite{moosavighazal}. Ghazal users rely on the Ethereum blockchain to register their \texttt{.ghazal} domain names and bind certificates to those names. In Ghazal model, a user would register domain name by executing the \textit{registerdomain} function from the Ghazal smart contract with the domain name in plain text as the function argument. As mentioned before, These transactions will sit in the mempool so that it would be mined by Ethereum miners and included in the block. During this period in which the transaction is not yet confirmed, front-running attack can occur by (i) dishonest miners and/or (ii) regular non-miner user. In the first case, a miner would intercept the \textit{registerdomain} transaction and register that name ahead of the user. A regular non-miner node in the Ethereum network can front-run other user's \textit{registerdomain} at a good profit by paying higher transaction fees. This practice allows the adversarial party  to register an unregistered domain immediately after someone searched for it, and sell the domain name to the users for a higher price. Note that, domain name front-running also occurs in the vanilla system. In this case, front-runners would monitor and identify domain names of interest, and sell it back to the other users with a higher price~\cite{sac022en33:online}.

@@

@@

@@

%Possibly remove this figure due to page limit
\begin{figure}[h]
\centering
\includegraphics[width=0.4\linewidth]{figures/cryptokittie842912.png}
\caption{ Cryptokitty Number 842912 \label{fig:cryptokittie}}
\end{figure}

@@

\subsubsection{Design Decision \#1: Commitment Scheme\newline} \label{CommitmentScheme} %talk about the drawbacks of this scheme: eg: you may forget to reveal. 
Commitment scheme is a cryptographic primitive that enables one to commit to a value --binding-- (\eg statement, document, data, \etc) while keeping it a secret and reveal the committed value on a later time~\cite{brassard1988minimum}. Commitment scheme is a robust method to prevent information leakage from the sensitive transactions. This could be done by simply broadcasting the hash value of the committed data and later on revealing the values that would be hashed to the committed hash, see Figure~\ref{fig:commitReveal}. 
In the case of decentral exchanges, user can send a commit transaction which will be cryptic to network participants but will act as a placeholder in the queue for the user, after the transaction is mined, user sends reveal transaction revealing the order details which will be executed in a fair order. Depending on the Dapp design, either the order is collateralized, which means the commitment transaction includes the funds required for fulfilling the order, which will leak some information about the order, or is not collateralized and opens up the possibility of user never revealing the commitment, which will be considered as a DoS attack. 
Another use of such commitment scheme, is in decentralized naming systems, such as Ghazal or ENS. In this case, a user would send a commit transaction similar to a sealed bid, once the transaction is confirmed and the grace period is over, user would send a reveal transaction revealing the bid and also the details of the requested domain. Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running. Similar approach applies to on-chain voting as well ~\cite{adChainPLCRVoting}, using sealed votes, voters can make sure their votes are hidden until a later date, however their participation and weight of the vote are publicly known. 
Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor. For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, It will be obvious that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme. Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design. On the other note, these method has some drawbacks, the user experience is not smooth and one might forget to reveal the committed transaction. In ENS commit-reveal process, if one forgets to reveal on the reveal phase, the committed funds are burnt and inaccessible there after. Also this scheme means two transaction are required for a functionality which is makes it more expensive to run.

@@

The details of how Submarine commitments work is outside the scope of this paper, however in summary, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality it is possible to generate one outgoing transaction from an address in which no private key exists. By constructing a transaction from that address to the DApp and funding that address we fulfil the commitment phase and by revealing the details and broadcasting the constructed transaction we reveal the commitment ~\cite{libsubmarine}, see Figure~\ref{fig:LibSubmarine}.  Drawbacks of this scheme are similar to ~\ref{CommitmentScheme}, with an addition of two more transactions to finalize the functionality, which results in more cost and complicated user experience.

@@

%Possibly remove this code snippet due to page limit
\begin{lstlisting}[basicstyle=\scriptsize\ttfamily,caption={Code snippet from LocalEthereum smart contract. Values V,R and S are set by LocalEtherem to have a valid signature, also the tradeHash uses buyer and seller addresses, mitigating the possibility of front-running by a third party.},label={code:localethereum},float]
    function createEscrow(bytes16 _tradeID, address _seller, address _buyer, uint256 _value, uint16 _fee,
					uint32 _paymentWindowInSeconds, uint32 _expiry, uint8 _v, bytes32 _r, bytes32 _s) 
        payable external {
        bytes32 _tradeHash = keccak256(abi.encodePacked(_tradeID, _seller, _buyer, _value, _fee));
	...
        // A signature (v, r and s) must come from localethereum to open an escrow
        bytes32 _invitationHash = keccak256(abi.encodePacked(
            _tradeHash,
            _paymentWindowInSeconds,
            _expiry
        )); 
\end{lstlisting}
